models with mice

### 2024-03-23 withmice.Rmd
put extra imputation tests etc for mice into another file

# missing data pattern and MCAR

@@

mcar_test(data= codedmodule2)

# p value = 1, which means MAR condition is met.

@@

# Kahan scale: MAR condition and missing data pattern 
```{r, echo=FALSE}

@@

## Mifa for Kahan scale 
```{r, echo =FALSE}

@@

## Pretty Table: FA Kahan

@@

## checking merging of imputations  : kahan scale

@@

#Kahan Factor scores: mean across all imputations

@@

## Kahan corelation table
```{r}

@@

# Kahan alpha test

@@

@@

# Eco-pol scale: MAR condition and missing data pattern

## Mifa for new eco-pol value scale : Nuclear energy

#Ecopol Factor scores: mean across all imputations

# Eco-pol alpha test

# Eco-pol: Radar map

# Pretty table: Nuclear EFA

@@

## State Ns before MIFA

## State Ns after MIFA on two scales

@@

# Mean across imputations

## LMs with final imputed datasets from FAs

@@

# interaction vars

```
\newpage

# NUCLEAR2 : only charcateristics of tech

# Nuclear2 : Mifa for new eco-pol value scale

miecopoln2 <- mifa(data= ecopoln2,
                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=10,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

# Solar : MAR condition and missing data pattern

# Solar : Mifa for new eco-pol value scale

# Solar 2 : only charcateristics of tech

# SOLAR2 : Mifa for new eco-pol value scale

# Solar: Mifa with CFA

>>>>

# FORMICE DATASET

@@

#mcar_test(data= codedmodule2)
# p value = 1, which means MAR condition is met.

@@

# Kahan scale

## MAR condition and missing data pattern 
```{r, echo=FALSE}

@@

## Mifa
```{r, echo =FALSE}

@@

## EFA Pretty Table

@@

## merging of imputation

@@

## Kahan Factor scores (mean across all imputations)

@@

## corelation table
```{r}

@@

## Alpha test

@@

# Nuclear: Eco-pol scale

## MAR condition and missing data pattern

## Mifa

## Factor Scores (mean across all imputations)

## Alpha test

## Radar map

## Pretty table: Nuclear EFA

# State Ns before MIFA

# State Ns after MIFA

## Nuclear: Ecopol (Mean across imputations)

# LMs : final imputed datasets

# interaction vars tablle

# Stargazer : all LMs

\newpage
# Paper 2

## NUCLEAR2

### only charcateristics of tech

### Nuclear2 : Mifa

library(mifa)

miecopoln2 <- mifa(data= ecopoln2,
                cov_vars = -c("age", "gender", "caste", "State", "urban_rural", "religion"),
                m=50,
                n_pc= 2:4,
                ci = "fieller", 
                n_boot=1000,
                print = FALSE,
                progress= TRUE, 
                seed = 528,)

### Factor Scores (mean across all imputations)

ecopoln2scores <- mice::complete(mice::mice(ecopoln2, m = 50, seed = 429, print = FALSE), "broad")

ecopoln2scores <- ecopoln2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

ecopoln2means <- ecopoln2scores %>%
  rowwise() %>%
  mutate(DEVNUCLEAR_mean = mean(c_across(starts_with("DEVNUCLEAR"))),
         PROSPERNUCLEAR_mean = mean(c_across(starts_with("PROSPERNUCLEAR"))),
         NPRIDENUCLEAR_mean = mean(c_across(starts_with("NPRIDENUCLEAR"))),
         PRIDENUCLEAR_mean = mean(c_across(starts_with("PRIDENUCLEAR"))),
         JOBSNUCLEAR_mean = mean(c_across(starts_with("JOBSNUCLEAR"))),
         RELYNUCLEAR_mean = mean(c_across(starts_with("RELYNUCLEAR"))),
         BEAUTYNUCLEAR_mean = mean(c_across(starts_with("BEAUTYNUCLEAR"))),
         HEALTHNUCLEAR_mean = mean(c_across(starts_with("HEALTHNUCLEAR"))),
         POLLUTENUCLEAR_mean = mean(c_across(starts_with("POLLUTENUCLEAR"))),
         DISPLACENUCLEAR_mean = mean(c_across(starts_with("DISPLACENUCLEAR"))),
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

necopol2final <- data.frame(factor.scores(ecopoln2means[, 1:10], ecopolfitn2)$scores)

### LM : Nuclear 2 and Kahan

ecopoln2final <- necopol2final %>%
  rename(DevPride = MR1, SocialCosts = MR2)

n2allfinal <- cbind(formice1,ecopoln2final, kahannuclearfinal)%>%
   mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
         Netben_Solar = Ben_Solar - Risky_Solar,
         Netben_Coal = Ben_Coal - Risky_Coal)

nuclear2lm <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(nuclear2lm)

netnuclear2lm <- lm(Netben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(netnuclear2lm)

bennuclear2lm <- lm(Ben_Nuclear ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(bennuclear2lm)

## Solar

### Solar : MAR condition and missing data pattern

### Solar : Mifa for new eco-pol value scale

### Solar 2 : only charcateristics of tech

### SOLAR2 : Mifa for new eco-pol value scale

### Factor Scores (mean across all imputations)

ecopols2scores <- mice::complete(mice::mice(ecopols2, m = 50, seed = 429, print = FALSE), "broad")

ecopols2scores <- ecopols2scores %>%dplyr::select(-(contains(c("age", "urban_rural", "gender","caste","religion", "State"))))

ecopols2means <- ecopols2scores %>%
  rowwise() %>%
  mutate(DEVSOLAR_mean = mean(c_across(starts_with("DEVSOLAR"))),
         PROSPERSOLAR_mean = mean(c_across(starts_with("PROSPERSOLAR"))),
         NPRIDESOLAR_mean = mean(c_across(starts_with("NPRIDESOLAR"))),
         PRIDESOLAR_mean = mean(c_across(starts_with("PRIDESOLAR"))),
         JOBSSOLAR_mean = mean(c_across(starts_with("JOBSSOLAR"))),
         RELYSOLAR_mean = mean(c_across(starts_with("RELYSOLAR"))),
         BEAUTYSOLAR_mean = mean(c_across(starts_with("BEAUTYSOLAR"))),
         HEALTHSOLAR_mean = mean(c_across(starts_with("HEALTHSOLAR"))),
         POLLUTESOLAR_mean = mean(c_across(starts_with("POLLUTESOLAR"))),
         DISPLACESOLAR_mean = mean(c_across(starts_with("DISPLACESOLAR"))),
  ) %>%
  ungroup()%>%
  dplyr::select(contains("_mean")) %>%
   rename_with(~ gsub("_mean$", "", .x))

secopol2final <- data.frame(factor.scores(ecopols2means[, 1:10], ecopolfits2)$scores)

### Solar LMs
```{r}

ecopols2final <- secopol2final %>%
  rename(DevPride = MR1, SocialCosts = MR2)

s2allfinal <- cbind(formice1,ecopols2final, kahannuclearfinal)%>%
   mutate(Netben_Nuclear = Ben_Nuclear - Risky_Nuclear,
         Netben_Solar = Ben_Solar - Risky_Solar,
         Netben_Coal = Ben_Coal - Risky_Coal)

solar2lm <- lm(Risky_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian , data = n2allfinal)

summary(solar2lm)

netsolar2lm <- lm(Netben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(netsolar2lm)

bensolar2lm <- lm(Ben_Solar ~ Uppercaste + Male + Hindu +Age + State + DevPride + SocialCosts + Egalitarian + Communitarian, data = n2allfinal)

summary(bensolar2lm)

### Solar: Mifa with CFA

# EXTRA

@@

@@

@@

@@
